### 2018-09-28 paper/paper.tex
Update basic notation and definitions

Which segments are viable complementary pairs to $P_i$? The only constraint on location is that an RNA molecule cannot form a loop of two or fewer nucleotides. Let $A_i$ be the set of all segments that are potential pairs of $P_i$:
\begin{equation}
A_i = \{P_j: 1 \leq j \leq i - 7 \text{ or }i + 7 \leq j \leq N - 3\}
\end{equation}
We can now define the {\em local ambiguity function}, 
\[
a(p) = (a_1(p), \cdots, a_{N - 3}(p))
\]
which is a vector-valued function of the primary structure $p$. The vector has  one component, $a_i(p)$, for each segment $P_i$, which is, simply, the number of feasible segments that are complementary to $P_i$:
\begin{align}
 a_i (p)& =  \# \{ P \in A_i : P \text{ and }P_i \text{ are complementary} \}  
 \\
& = 
\#\big\{P_j\in A_i:  (P_{i, k}, P_{j, 5 - k}) \in \{ (A, U), (U, A), (G, C), (C, G), (G,U), (U,G) \},
\nonumber \\
&  \ \ \ \ \ \ \ \ k=1,\ldots,4 \big\} 
\nonumber 
\end{align}

@@

Formally, given a secondary structure $s$, as defined in equation (2), and a location $i\in\{1, 2,\ldots,N-3\}$, let $f_i(s)$ be the number of nucleotides in $P_i$ that are paired under $s$:
\begin{equation}
f_i(s) = \#\{j\in P_i:(j,k)\in s\text{ or } (k,j)\in s, \text{ for some } 1\leq k \leq N\}
\end{equation}
Evidently, $0\leq f_i(s)\leq 4$. The ``paired nucleotides function'' is then the 
vector-valued function of secondary structure defined as 
$f(s)=(f_1(s),\ldots,f_{N-3}(s))$.
Finally, we use $f$ to distinguish three types of locations (and hence three types of segments): location $i$ will be labeled 
\begin{equation}
	\begin{cases}
		\text{\textit{single} if } f_i(s) = 0 \\
		\text{\textit{double} if } f_i(s) = 4 \\
		\text{\textit{transitional} if } 0 < f_i(s) < 4
	\end{cases} i = 1, 2, \cdots, N - 3
\end{equation}

>>>>

Which segments are viable complementary pairs to $P_i$? The only constraint on location is that an RNA molecule cannot form a loop of two or fewer nucleotides. Let $A_i$ be the set of all segments that are potential pairs of $P_i$:
\begin{equation}
A_i = \{P_j: 1 \leq j \leq i - 7 \text{ or }i + 7 \leq j \leq N - 3\}
\end{equation}
We can now define the {\em local ambiguity function}, 
\[
a(p) = (a_1(p), \cdots, a_{N - 3}(p))
\]
which is a vector-valued function of the primary structure $p$. The vector has  one component, $a_i(p)$, for each segment $P_i$, which is, simply, the number of feasible segments that are complementary to $P_i$:
\begin{align}
 a_i (p)& =  \# \{ P \in A_i : P \text{ and }P_i \text{ are complementary} \}  
 \label{eqn:LocalAmbiguity} \\
& = 
\#\big\{P_j\in A_i:  (P_{i, k}, P_{j, 5 - k}) \in \{ (A, U), (U, A), (G, C), (C, G), (G,U), (U,G) \},
\nonumber  \\
&  \ \ \ \ \ \ \ \ k=1,\ldots,4 \big\} 
\nonumber 
\end{align}

@@

Formally, given a secondary structure $s$, as defined in Eq (2), and a location $i\in\{1, 2,\ldots,N-3\}$, let $f_i(s)$ be the number of nucleotides in $P_i$ that are paired under $s$:
\begin{equation}
f_i(s) = \#\{j\in P_i:(j,k)\in s\text{ or } (k,j)\in s, \text{ for some } 1\leq k \leq N\}
\end{equation}
Evidently, $0\leq f_i(s)\leq 4$. The ``paired nucleotides function'' is then the 
vector-valued function of secondary structure defined as 
$f(s)=(f_1(s),\ldots,f_{N-3}(s))$.
Finally, we use $f$ to distinguish three types of locations (and hence three types of segments): location $i$ will be labeled 
\begin{equation}
	\begin{cases}
		\text{\textit{single} if } f_i(s) = 0 \\
		\text{\textit{double} if } f_i(s) = 4 \\
		\text{\textit{transitional} if } 0 < f_i(s) < 4
	\end{cases} i = 1, 2, \cdots, N - 3
\end{equation}
